Visual proteomics using whole-lamella 2D template matching

### 2022-03-30 manuscript.tex
Merge branch 'main' of github.com:jojoelfe/deco_lace_template_matching_manuscript into main [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/2d0a9a5debbbf44b5f9d5797d38db68589012013.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/2d0a9a5debbbf44b5f9d5797d38db68589012013/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/2065944123

This manuscript
(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/0a724b0da1586e2992e709189796c245a3f07ccf/}{permalink})
was automatically generated
from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/0a724b0da1586e2992e709189796c245a3f07ccf}{jojoelfe/deco\_lace\_template\_matching\_manuscript@0a724b0}
on March 29, 2022.

>>>>

This manuscript
(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/2d0a9a5debbbf44b5f9d5797d38db68589012013/}{permalink})
was automatically generated
from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/2d0a9a5debbbf44b5f9d5797d38db68589012013}{jojoelfe/deco\_lace\_template\_matching\_manuscript@2d0a9a5}
on March 30, 2022.
